---
title: "MIS581-Portfolio Project Code"
author: "Prakash Bajracharya"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
# Section -  Data exploration


```{r data exploration}
# Loading necessary library

library(dplyr)
library(ggplot2)

#Dataset Statistical Summary

## Loading banking data into data frame

bank_df <- read.csv("F:/LearningStuff/CSUGLOBAL/MIS-581/bank-additional-full.csv")

## Viewing all data in the data frame
View (bank_df)

## Displaying the structure
str(bank_df)

## Statistical Summary for all the attributes in the data frame
summary(bank_df)

## First 6 (default) rows of the data frame
head(bank_df)

## Getting dimension of the data frame
dim(bank_df)

## attributes name in data frame
names(bank_df)

## Calculate additional descriptive statistics for numerical data
bank_df %>%
  summarise(across(where(is.numeric), list(mean = mean, sd = sd, median = median)))
### data frame with 0 columns and 1 row
## Count frequencies of categorical data
bank_df %>%
  summarise(across(where(is.factor), ~table(.)))
### data frame with 0 columns and 1 row


# Hypothesis Testing

## Converting columns to factor for proper statistical analysis and visualization
bank_df$contact <- as.factor(bank_df$contact)
bank_df$y <- as.factor(bank_df$y)
bank_df$age <- as.numeric(bank_df$age)

## Hypothesis 1: Method of contact
contact_effect <- table(bank_df$contact, bank_df$y)
contact_test <- chisq.test(contact_effect)
contact_test

## Plotting the results
ggplot(bank_df, aes(x = contact, fill = y)) +
  geom_bar(position = 'fill') +
  labs(title = 'Subscription Rate by Contact Method', y = 'Proportion', x = 'Contact Method')


## Hypothesis 2: Age effect
age_groups <- bank_df %>%
  mutate(age_group = cut(age, breaks = c(18, 35, 60, 100), labels = c('18-35', '36-60', '60+'))) %>%
  group_by(age_group, y) %>%
  summarise(count = n()) %>%
  ungroup()

age_effect <- chisq.test(table(age_groups$age_group, age_groups$y))
age_effect

## Plotting the results
ggplot(age_groups, aes(x = age_group, y = count, fill = y)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(title = 'Subscription Rate by Age Group', y = 'Count', x = 'Age Group')


## Hypothesis 3: Previous engagement
bank_df$previous <- as.factor(ifelse(bank_df$previous > 0, 'yes', 'no'))
previous_effect <- table(bank_df$previous, bank_df$y)
previous_test <- chisq.test(previous_effect)
previous_test

## Plotting the results
ggplot(bank_df, aes(x = previous, fill = y)) +
  geom_bar(position = 'fill') +
  labs(title = 'Subscription Rate by Previous Engagement', y = 'Proportion', x = 'Previous Engagement')


